Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-02-16 ms.tex
Repeated the long dark experiment for grism-like aperture and renamed dark files

\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.32\columnwidth]{ap_labels_dark_NRCALONG-DARK-7235074213_1.pdf}
\includegraphics[width=.32\columnwidth]{ap_labels_darkRed_NRCALONG-DARK-7235074213_1.pdf}
\includegraphics[width=.32\columnwidth]{ap_labels_darkRedRowColSub_NRCALONG-DARK-7235074213_1.pdf}
\includegraphics[width=.32\columnwidth]{long_dark_Raw.pdf}
\includegraphics[width=.32\columnwidth]{long_dark_Reduced.pdf}
\includegraphics[width=.32\columnwidth]{long_dark_ReducedRowColSub.pdf}
\caption{Time series of a 70 pixel radius photometric aperture obtained during a long dark exposure for detector ALONG=A5. The long dark exposure of 108 frames is used to construct 54 pairs of reads that are subtracted, in analogy with a series of integrations.
{\it Top:}  Example read pair subtraction with an overlay of the apertures for 3 different reduction steps from "Raw" data using no reference pixel correction, "Reduced Data" using reference pixels and "ReducedRowColSub" using reference pixels and background subtraction for each row and each column.
{\it Bottom} The time series for each circular aperture with background subtraction using a circular annulus.
The most important step for reducing the noise in the time series is row-by-row subtraction to remove the 1/f noise.
}\label{fig:longDarkPhot}
\end{figure*}

@@

\subsection{Grism Aperture}
\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.4\columnwidth]{ap_labels_darkGrismApA5raw_NRCALONG-DARK-7235074213_1.pdf}
\caption{Time series of a grism photometric broadband aperture during a long dark exposure for detector ALONG=A5. As in \ref{fig:longDarkPhot}, the long dark exposure of 108 frames is used to construct 54 pairs of reads that are subtracted, in analogy with a series of integrations.
The photometric aperture is made to represent a similar one to the F322W2 grism trace.
}\label{fig:longDarkGrism}
\end{figure*}

>>>>

\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.32\columnwidth]{ap_labels_dark_NRCALONG-DARK-7235074213_1.pdf}
\includegraphics[width=.32\columnwidth]{ap_labels_darkRed_NRCALONG-DARK-7235074213_1.pdf}
\includegraphics[width=.32\columnwidth]{ap_labels_darkRedRowColSub_NRCALONG-DARK-7235074213_1.pdf}
\includegraphics[width=.32\columnwidth]{long_dark_dark.pdf}
\includegraphics[width=.32\columnwidth]{long_dark_darkRed.pdf}
\includegraphics[width=.32\columnwidth]{long_dark_darkRedRowSub.pdf}
\caption{Time series of a 70 pixel radius photometric aperture obtained during a long dark exposure for detector ALONG=A5. The long dark exposure of 108 frames is used to construct 54 pairs of reads that are subtracted, in analogy with a series of integrations.
{\it Top:}  Example read pair subtraction with an overlay of the apertures for 3 different reduction steps from "Raw" data using no reference pixel correction, "Reduced Data" using reference pixels and "ReducedRowColSub" using reference pixels and background subtraction for each row and each column.
{\it Bottom} The time series for each circular aperture with background subtraction using a circular annulus.
The most important step for reducing the noise in the time series is row-by-row subtraction to remove the 1/f noise.
}\label{fig:longDarkPhot}
\end{figure*}

@@

\subsection{Grism Aperture}
\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.32\columnwidth]{g00_ap_labels_darkGrismApA5raw_NRCALONG-DARK-7235074213_1}
\includegraphics[width=.32\columnwidth]{g01_ap_labels_darkGrismApA5red_NRCALONG-DARK-7235074213_1}
\includegraphics[width=.32\columnwidth]{g02ap_labels_darkGrismApA5redRowCol_NRCALONG-DARK-7235074213_1}
\includegraphics[width=.32\columnwidth]{long_dark_darkGrismApA5raw.pdf}
\includegraphics[width=.32\columnwidth]{long_dark_darkGrismApA5red.pdf}
\includegraphics[width=.32\columnwidth]{long_dark_darkGrismApA5redRowCol.pdf}
\caption{Time series of a grism photometric broadband aperture during a long dark exposure for detector ALONG=A5. As in \ref{fig:longDarkPhot}, the long dark exposure of 108 frames is used to construct 54 pairs of reads that are subtracted, in analogy with a series of integrations.
The photometric aperture is made to represent a similar one to the F322W2 grism trace.
}\label{fig:longDarkGrism}
\end{figure*}
